---
title: "WGSA parsing demo"
output: html_notebook
---

Documenting my workflow:

Install tools:
```{r}
library(devtools)
devtools::install_github("UW-GAC/wgsaparsr")
library(wgsaparsr)
```

First, let's look at this WGSA output file and see what we're working with:
```{r}
readLines("snp.tsv.gz", n=2)
```

Hrm. Not super pretty. I've made a function in wgsaparsr to make listing the fields prettier, though:
```{r}
# list all fields in an annotation file: 
get_fields("snp.tsv.gz")
```

That's lots of fields. We don't need them all for our current purposes, so select a subset of the fields from source file:

(note that the VEP_ensembl_* fields are complex, so need to be parsed further to make tidy)
```{r}
desired_columns <- 
  c(
    "#chr",
    "pos",
    "ref",
    "alt",
    "rs_dbSNP147",
    # "CADDphred",
    "CADD_phred", #NOTE: different than the indel annotation file.
    "VEP_ensembl_Transcript_ID",
    "VEP_ensembl_Gene_Name",
    "VEP_ensembl_Gene_ID",
    "VEP_ensembl_Consequence",
    "VEP_ensembl_Amino_Acid_Change",
    "VEP_ensembl_LoF",
    "VEP_ensembl_LoF_filter",
    "VEP_ensembl_LoF_flags",
    "VEP_ensembl_LoF_info"
    # "1000Gp3_AF" #skipped for the workshop because code doesn't work with this variable name
    )
    
    to_split <-
    c(
    "VEP_ensembl_Consequence",
    "VEP_ensembl_Transcript_ID",
    "VEP_ensembl_Gene_Name",
    "VEP_ensembl_Gene_ID",
    "VEP_ensembl_Amino_Acid_Change",
    "VEP_ensembl_LoF",
    "VEP_ensembl_LoF_filter",
    "VEP_ensembl_LoF_flags",
    "VEP_ensembl_LoF_info"
    )
  

```

Now, let's look at that parsed WGSA file:


NOTE: the CADD phred score field is different in the indel file than the snp annotation file. In the snp file, it's CADD_phred; in the indel file it's CADDphred.

```{r}
desired_columns_indel <- 
  c(
    "`#chr`",
    "pos",
    "ref",
    "alt",
    "rs_dbSNP147",
    "CADDphred",
    #  "CADD_phred", #NOTE: different than the general annotation file.
    "VEP_ensembl_Transcript_ID",
    "VEP_ensembl_Gene_Name",
    "VEP_ensembl_Gene_ID",
    "VEP_ensembl_Consequence",
    "VEP_ensembl_Amino_Acid_Change",
    "VEP_ensembl_LoF",
    "VEP_ensembl_LoF_filter",
    "VEP_ensembl_LoF_flags",
    "VEP_ensembl_LoF_info"
    # "1000Gp3_AF"#skipped for the workshop because code doesn't work with this variable name
    )
  
parse_indel_to_file("indel.tsv.gz", "parsed_indel.tsv", desired_columns_indel, to_split, verbose = TRUE)
```

Check the parsed WGSA indel file:

```{r}
readLines("parsed_indel.tsv", n=2)
```

Also not super pretty. Listing the fields:
```{r}
# list all fields in an annotation file: 
get_fields("parsed_indel.tsv")
```
